---
title: "`r dat$title`"
author: 
- affiliation: "`r dat$affiliation`"
  email: "`r dat$email_address`"
  name: "`r dat$requester_name`"
addr: 
  l1: "`r dat$x24_7_contact_phone_number`"
output: 
  word_document: 
      reference_docx: styles_reference.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```


### **Requester:** `r dat$requester_name` (`r dat$email_address`; `r dat$x24_7_contact_phone_number `)

### **Affiliation:** `r dat$affiliation`

## General Information

**`r maxyr` GF `r dat$survey `**

   - *Is this a new or a repeat collection?:* `r dat$new_or_repeat_collection `
   - *Collection type:* `r dat$collection_type `       
   - *Project Funding Source:* `r dat$funding `
   - *Is this project funding extra sea days?* `r dat$extra_sea_days `
   - *Is this project funding fuel costs?* `r dat$fuel_costs `

**Project Description and Justification:** `r dat$goals_and_justification`

```{r}
```

## Detailed Collection Procedures

**Detailed Collection Procedures:** `r dat$detailed_collection_procedures`

**Subsample Selectively:** `r dat$criteria_for_selecting_specimens` 

**Estimated time:** `r dat$estimated_time`

## Biological Collection Details

   - *Species To Be Collected:* `r dat$animal_type``r ifelse(is.na(dat$species_name), "", paste0("  - ", dat$species_name))`
   - *Type of specimen to collect:* `r dat$specimen_type`
   - *Specimen-level data to collect:* `r dat$specimen_data`
   - *Specimen preservation method:* `r dat$specimen_preservation_method`

```{r}
```

## Sampling Design Details

**Target Quantity:** `r dat$target `

**Will the request still be useful if the requested amount or frequency of specimens collected is not achieved?** `r dat$if_the_requested_amount_or_frequency_of_specimens_is_not_achieved_will_the_request_still_be_useful `

**What is the sampling protocol:** `r dat$sampling_design`

**Criteria for sub-sampling if selective or stratified sub-sampling:** `r dat$criteria_for_selecting_specimens`

## Geographic Region of Collection

**Survey:** `r dat$survey`

**Place keywords:** `r dat$place_keywords`

**Bounding coordinates**

  - *Northern Boundary:* `r dat$northern_boundary`
  - *Southern Boundary:* `r dat$southern_boundary`
  - *Eastern Boundary:* `r dat$eastern_boundary`
  - *Western Boundary:* `r dat$western_boundary`

```{r}
```

## Chemicals, Supplies, Equipment, and Shipping

**Project Chemicals:**  

   - *Formaldehyde solutions:* `r dat$project_chemicals_formaldehyde `
   - *Ethanol solutions:* `r dat$project_chemicals_ethanol `
   - *glycerol/thymol:* `r dat$project_chemicals_glycerol_thymol `
   - *DNA buffer (DMSO/EDTA/NaCl):* `r dat$project_chemicals_dna_buffer_dmso_edta_na_cl `

**Project Supplies:** 

   - *Supplies provided by the AFSC:* `r dat$afsc_supplies `
   - *Supplies provided by the requester:* `r dat$requester_supplies ` 

**Detailed Shipping Instructions:** `r dat$detailed_shipping_instructions `

**Permits issued or pending:** `r dat$additional_permits_issued_or_pending `

